Adopting agile in the large: motivations, success factors and challenges

### 2014-05-15 journal/article.tex
Editing: Challenges in other functions

Agile methods are typically understood through a set of activities closely
related to software development. Cases describe how development teams were
typically the first entities in the organization that were considered when
introducing agile [P2, P17, P31, P38]. However, development operates in a larger
context, and will need to interface with other organizational functions.
Challenges were faced when exposing other parts of the organization to the agile
mode, and functions that were further away from development were resistant to
change [P2, P18, P31]. A tension was growing between development and broader
roles in the organization [P1]. The full beenfits of the transformation would
not be attained unless the entire organization was set to work along the same
paradigm [P18, P42].

Primary sources listed various functions beyond development that are involved in
bringing products to the market. Marketing was a particularly frequently
mentioned group [P5, P17, P28, P31, P38, P45, P48]. Other groups involved in the
whole of product delivery were sales [P17, P31], infrastructure and operations
[P10, P45, P46, P50], user experience and design [P9, P10, P28], documentation
[P28], legal [P10], security [P10], customer services [P48], and finance [P48].
All of these groups were reported to be affected on some level by the agile
transformation.

>>>>

Agile methods are typically considered as a set of activities closely related to
software development. Cases describe how development teams were the first
entities in the organization that were considered when introducing agile [P2,
P17, P31, P38]. However, development operates in a larger context and will need
to interface with other organizational functions.
Challenges were faced when exposing other parts of the organization to the agile
model, and functions that were further away from development were resistant to
change [P2, P18, P31]. A tension was growing between development and broader
roles in the organization [P1]. The full beenfits of the transformation would
not be attained unless the entire organization was set to work along the same
paradigm [P18, P42].

Primary sources listed various functions beyond development that are involved in
bringing products to the market. Functions interfacing with development and
affected by the agile transformation are presented in figure
\ref{fig:challenges_other_functions}.
Marketing was a particularly frequently mentioned group [P5, P17, P28, P31, P38,
P45, P48]. Other groups involved in the whole of product delivery were sales
[P17, P31], infrastructure and operations [P10, P45, P46, P50], user experience
and design [P9, P10, P28], documentation [P28], legal [P10], security [P10],
customer services [P48], and finance [P48].

\begin{figure}
  \begin{center}
    \includegraphics{graphics/challenges_other_functions.pdf}
    \caption{Functions affected by the agile transformation}
    \label{fig:challenges_other_functions}
  \end{center}
\end{figure}
